author: "Sofia Ingersoll"
title: "Adaptation Observatory: Survey Response Demographics (Bangladesh & India)"
date: 2024-4-14
format:
  html:
    code-fold: true
    code-summary: "Show the code"
#embed-resources: true
---

## Set Up

```{r message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

#..........................load packages.........................
library(tidyverse)        # load the tidyverse package to assist with data wrangling & cleaning 

library(patchwork)        # load the patchwork package to assist in plot composition (displaying multiple data visualizations) 

library(showtext)         # load the showtext to more easily use fonts
library(here)

library(leaflet)
library(osmextract) 
library(units)
library(sf)
library(sfheaders)
library(sp)
library(raster)
library(tmap)
library(terra)
library(stars)
library(ggtext)
library(units)

library(tidyverse)
library(treemap)
library(sunburstR)
library(purrr)
```

## Load & Wrangle Survey Demographic Data
```{r warning = FALSE}
bgd_file <- file.path(here("..","data","adapt_observ_survey_responses", "Observatory_Bangladesh_2024_04_15.csv"))
  
ind_file <- file.path(here("..","data","adapt_observ_survey_responses", "Observatory_India_2024_04_15.csv"))

bgd_responses <- read_csv(bgd_file, show_col_types = FALSE)
  
ind_responses <-read_csv(ind_file, show_col_types = FALSE)
