---
title: "Descriptive Demographic Response Distributions"
author: "Sofia Ingersoll"
output:
  html-document:
    code_folding: show
    toc: true
    toc_float: true
editor: 
  markdown: 
    wrap: 72
---

# Adaptation Observatory Responses

## India & Bangladesh

### 2024 April 15

#### Overview & Goals

**Create a function to save these histograms for each category as png in
a folder to look at later** - Visuals of the response distributions from
each demo. group - Visualizing the difference in the responses from
those duplicates

-   Isolate quality respondents, their locations and the boundary of
    cell tower locations

-   Break down of each topic, then note the ones with the greatest
    variation

-   i should create break downs of each demogs, responses as it’s own
    histogram

-   so function to sort by gender and age, then display other things

-   also have one just for gender age + demo gender age

#### Set up

```{r}
library(here)
library(tidyverse)
library(RColorBrewer)
```

```{r}
# load BGD data 
bgd <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
# group duplicated by phone & ip
bgd_dup <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE) 


# load IND data 
ind <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
# group duplicated by phone & ip
ind_dup <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE) 
```

IDEAS

```{r}
colnames(ind)
```

GROUP BY AGE & GENDER: DISPLAY COUNT OF ANSWER subset data or select
group

x = answer y = count

GROUPING BY GENDER AND AGE GROUPS

Age groups: age \>= 18 & age \< 30 age \>= 30 & age \< 50 age \>= 50

color = gender

#### BGD

```{r}
# data wrangling
plot_data_bgd <- bgd %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(age_group, gender, demo_gender, demo_age, age,
         q_language, income_brackets, demo_income,
         household_move, flood_year, stay_residence,
         flood_close, move_rural_urban, property_loss,
         housing_damage, flood_prepared, contact_authority,
         enough_eat, climate_problem, trust_government,
         region, no_surverys_submitted) 

# data wrangling
plot_data_bgd_dup <- bgd_dup %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(ip_address, comp_phone1_try1, age_group,
                gender, demo_gender, demo_age, age,
                q_language, income_brackets, demo_income,
                household_move, flood_year, stay_residence,
                flood_close, move_rural_urban, property_loss,
                housing_damage, flood_prepared, contact_authority,
                enough_eat, climate_problem, trust_government,
                no_surverys_submitted, region) 

plot_data_bgd
```

#### IND

```{r}
# data wrangling
plot_data_ind <- ind %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(age_group, gender, demo_gender, demo_age, age,
         q_language, income_brackets, demo_income,
         household_move, flood_year, stay_residence,
         flood_close, move_rural_urban, property_loss,
         housing_damage, flood_prepared, contact_authority,
         enough_eat, climate_problem, trust_government,
         no_surverys_submitted, region) 


# data wrangling
plot_data_ind_dup <- ind_dup %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(ip_address, comp_phone1_try1, age_group, gender, demo_gender, demo_age, age,
         q_language, income_brackets, demo_income,
         household_move, flood_year, stay_residence,
         flood_close, move_rural_urban, property_loss,
         housing_damage, flood_prepared, contact_authority,
         enough_eat, climate_problem, trust_government,
         no_surverys_submitted, region) 


plot_data_ind_dup
plot_data_ind
```

# Set up

```{r}
colors <- c("Female" = "#D16014", "Male" = "#17255A")
#"#C4A287"
```

# Function for plotting survey responses using clean df

```{r}
generate_plot <- function(df, country, survey_question, round_of_surveying) {
  # Create folder if it doesn't exist
  folder_path <- paste0(here("response_analysis","response_visuals"))
  if (!file.exists(folder_path)) {
    dir.create(folder_path)
    print(paste("Folder", folder_path, "created."))
  }

  # Save survey question as a title for plotting
  if (survey_question %in% names(df)) {
    # Modify survey question title
    survey_question_title <- tools::toTitleCase(survey_question)
    survey_question_title <- gsub("_", " ", survey_question_title)

    if ("Yes" %in% df[[survey_question]] | survey_question == "income_brackets" | survey_question == "region") {
      # Subset data for plotting 
      plot_data <- df %>%
        # label groups by age demo
        mutate(age_group = fct_reorder(age_group, .data[[survey_question]])) %>%
        mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
        # count frequency 
        group_by(age_group, gender, .data[[survey_question]]) %>%
        summarise(count = n()) %>%
        ungroup() %>% 
        # create histogram
        ggplot(aes(fill = gender, y = .data[[survey_question]], x= age_group)) + 
        geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
        labs(title = paste0(country, " ", survey_question_title, " Distribution in Age Demographics"),
             subtitle = paste0("Adaptation Observatory Survey Responses: ", round_of_surveying),
             x = "Age Demographic Groups",
             y = paste0("Count of ", survey_question_title)) +
        # count of language frequency 
        geom_text(aes(label = count,
                      fontface = "bold"),
                  size = 3,
                  position = position_dodge(width = 0.9),
                  hjust = .5,
                  vjust = -0.4,
                  color = "grey40") +
        # customs
        scale_fill_manual(values = colors) +
        theme_classic()  +
        theme(
          plot.title = element_text(size = 15,
                                    hjust = .5),
          plot.subtitle = element_text(size = 12,
                                       hjust = .5),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)) # Adjust y-axis title position
        ) 

      # Save plot as a png
      plot_filename <- paste0(folder_path, "/", round_of_surveying, "/", country, "_", survey_question, "_response_analysis_", round_of_surveying, ".png")
      ggsave(filename = plot_filename, plot = plot_data, width = 8, height = 5, dpi = 300)

      print("Plot saved successfully.")
    } else {
      # Subset data for plotting 
      plot_data <- df %>%
        # label groups by age demo
        mutate(age_group = fct_reorder(age_group, .data[[survey_question]])) %>%
        mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
        # count frequency 
        group_by(age_group, gender, .data[[survey_question]]) %>%
        summarise(count = n()) %>%
        ungroup() %>% 
        # create histogram
        ggplot(aes(fill = gender, y = .data[[survey_question]], x= age_group)) + 
        geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
        labs(title = paste0(country, " ", survey_question_title, " Distribution in Age Demographics"),
             subtitle = paste0("Adaptation Observatory Survey Responses: ", round_of_surveying),
             x = "Age Demographic Groups",
             y = paste0("Count of ",survey_question_title)) +
        # count of language frequency 
        geom_text(aes(label = count,
                      fontface = "bold"),
                  size = 3,
                  position = position_dodge(width = 0.9),
                  hjust = -1.5,
                  vjust = 0.4,
                  color = "grey40") +
        # customs
        scale_fill_manual(values = colors) +
        coord_flip() +
        theme_classic()  +
        theme(
          plot.title = element_text(size = 15,
                                    hjust = .5),
          plot.subtitle = element_text(size = 12,
                                       hjust = .5),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)) # Adjust y-axis title position
        )

      # Save plot as a png
      plot_filename <- paste0(folder_path, "/", country, "/", round_of_surveying, "/", country, "_", survey_question, "_response_analysis_", round_of_surveying, ".png")
      ggsave(filename = plot_filename, plot = plot_data, width = 10, height = 6, dpi = 300)

      print("Plot saved successfully.")
    } 
  } else {
    print("Specified survey question column does not exist in the dataframe.")
  }
}
```

```{r warning=FALSE, message=FALSE}
generate_plot(plot_data_ind, "IND", "climate_problem", "R1")
```

# Duplicates

```{r}
colnames(plot_data_ind_dup)

# this confirms that all of the respondants here have unique 
# 45 repeat
repeat_bgd <- as.numeric(length(unique(bgd_dup$response_id))) - as.numeric(length(unique(bgd_dup$comp_phone1_try1)))

# 6 repeat
repeat_ind <- as.numeric(length(unique(ind_dup$response_id))) - as.numeric(length(unique(ind_dup$comp_phone1_try1)))

# okay wait, i'm not confident in my approach above bc it's not looking at commonalities between the vectors
# let's try intersect()

ip_phone_combinations <- function(data) {
  
  # Find combinations that appear more than once
  duplicated_combinations <- data[duplicated(data[, c("ip_address", "comp_phone1_try1")]) |
                                  duplicated(data[, c("ip_address", "comp_phone1_try1")], fromLast = TRUE), 
                                  c("ip_address", "comp_phone1_try1")]
  return(duplicated_combinations)
}


# Example usage:
# Assuming 'bgd_dup' is your data frame
repeat_bgd <- ip_phone_combinations(bgd_dup)


repeat_ind <- ip_phone_combinations(ind_dup)



# using join, let's isolate all observations from duplicate phone + ip
bgd_duplicates <- inner_join(plot_data_bgd_dup, repeat_bgd, by = c("ip_address", "comp_phone1_try1"))

# save file
write.csv(bgd_duplicates, file = "../clean_data/adaptation_observatory_bgd_cleaned_duplicate_survey_questions_R1.csv")


# using join, let's isolate all observations from duplicate phone + ip
ind_duplicates <- inner_join(plot_data, repeat_ind, by = c("ip_address", "comp_phone1_try1"))


# save file
write.csv(ind_duplicates, file = "../clean_data/adaptation_observatory_ind_cleaned_duplicate_survey_questions_R1.csv")
```

# Duplicate Iteration Function

## This one to see overall duplicated data responses

```{r}
generate_dup_plot <- function(df, country, survey_question, round_of_surveying) {
  # Create folder if it doesn't exist
  folder_path <- paste0(here("response_analysis","response_visuals", country, round_of_surveying))
  if (!file.exists(folder_path)) {
    dir.create(folder_path)
    print(paste("Folder", folder_path, "created."))
  }

  # Save survey question as a title for plotting
  if (survey_question %in% names(df)) {
    # Modify survey question title
    survey_question_title <- tools::toTitleCase(survey_question)
    survey_question_title <- gsub("_", " ", survey_question_title)

    if ("Yes" %in% df[[survey_question]] | survey_question == "income_brackets" | survey_question == "region") {
      # Subset data for plotting 
      plot_data <- df %>%
        # label groups by age demo
        mutate(age_group = fct_reorder(age_group, .data[[survey_question]])) %>%
        mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
        # count frequency 
        group_by(age_group, gender, .data[[survey_question]]) %>%
        summarise(count = n()) %>%
        ungroup() %>% 
        # create histogram
        ggplot(aes(fill = gender, y = .data[[survey_question]], x= age_group)) + 
        geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
        labs(title = paste0(country, " ", survey_question_title, " Distribution in Age Demographics"),
             subtitle = paste0("Adaptation Observatory Survey Responses: ", round_of_surveying),
             x = "Age Demographic Groups",
             y = paste0("Count of ", survey_question_title)) +
        # count of language frequency 
        geom_text(aes(label = count,
                      fontface = "bold"),
                  size = 3,
                  position = position_dodge(width = 0.9),
                  hjust = .5,
                  vjust = -0.4,
                  color = "grey40") +
        # customs
        scale_fill_manual(values = colors) +
        theme_classic()  +
        theme(
          plot.title = element_text(size = 15,
                                    hjust = .5),
          plot.subtitle = element_text(size = 12,
                                       hjust = .5),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)) # Adjust y-axis title position
        ) 

      # Save plot as a png
      plot_filename <- paste0(folder_path, "/", "dup_data_vis","/","total_dup_response", "/", country, "_", survey_question, "_duplicates_response_analysis_", round_of_surveying,".png")
      ggsave(filename = plot_filename, plot = plot_data, width = 8, height = 5, dpi = 300)

      print("Plot saved successfully.")
    } else {
      # Subset data for plotting 
      plot_data <- df %>%
        # label groups by age demo
        mutate(age_group = fct_reorder(age_group, .data[[survey_question]])) %>%
        mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
        # count frequency 
        group_by(age_group, gender, .data[[survey_question]]) %>%
        summarise(count = n()) %>%
        ungroup() %>% 
        # create histogram
        ggplot(aes(fill = gender, y = .data[[survey_question]], x= age_group)) + 
        geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
        labs(title = paste0(country, " ", survey_question_title, " Distribution in Age Demographics"),
             subtitle = paste0("Adaptation Observatory Survey Responses: ", round_of_surveying),
             x = "Age Demographic Groups",
             y = paste0("Count of ",survey_question_title)) +
        # count of language frequency 
        geom_text(aes(label = count,
                      fontface = "bold"),
                  size = 3,
                  position = position_dodge(width = 0.9),
                  hjust = -1.5,
                  vjust = 0.4,
                  color = "grey40") +
        # customs
        scale_fill_manual(values = colors) +
        coord_flip() +
        theme_classic()  +
        theme(
          plot.title = element_text(size = 15,
                                    hjust = .5),
          plot.subtitle = element_text(size = 12,
                                       hjust = .5),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)) # Adjust y-axis title position
        )

      # Save plot as a png
      plot_filename <- paste0(folder_path, "/", "dup_data_vis","/","total_dup_response", "/", country, "_", survey_question, "_duplicates_response_analysis_", round_of_surveying,".png")
      ggsave(filename = plot_filename, plot = plot_data, width = 10, height = 6, dpi = 300)

      print("Plot saved successfully.")
    } 
  } else {
    print("Specified survey question column does not exist in the dataframe.")
  }
}
```

```{r}
generate_dup_plot(ind_duplicates, "IND", "q_language", "R1")
```

## This one to iterate by ip

```{r}
generate_dup_plots <- function(df, country, survey_question, round_of_surveying) {
  # Create folder if it doesn't exist
  folder_path <- paste0(here("response_analysis","response_visuals"))
  if (!file.exists(folder_path)) {
    dir.create(folder_path)
    print(paste("Folder", folder_path, "created."))
  }
  
  # Save survey question as a title for plotting
  if (survey_question %in% names(df)) {
    # Modify survey question title
    survey_question_title <- tools::toTitleCase(survey_question)
    survey_question_title <- gsub("_", " ", survey_question_title)
    
    # Group by IP address and comp_phone1_try1
    grouped_df <- df %>%
      group_by(ip_address, comp_phone1_try1) %>%
      summarise()
    
    # Iterate over each group and generate individual histograms
    for (i in 1:nrow(grouped_df)) {
      ip <- grouped_df$ip_address[i]
      phone <- grouped_df$comp_phone1_try1[i]
      
      # Subset data for the current group
      plot_data <- df %>%
        filter(ip_address == ip, comp_phone1_try1 == phone) %>%
        # label groups by age demo
        mutate(age_group = fct_reorder(age_group, .data[[survey_question]])) %>%
        mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+", NA))) %>%
        # count frequency 
        group_by(age_group, gender, .data[[survey_question]]) %>%
        summarise(count = n()) %>%
        ungroup() %>% 
        # create histogram
        ggplot(aes(fill = gender, y = .data[[survey_question]], x= age_group)) + 
        geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
        labs(title = paste0(country, " ", survey_question_title, " Distribution in Age Demographics"),
             subtitle = paste0("Adaptation Observatory Survey Responses: ", round_of_surveying),
             x = "Age Demographic Groups",
             y = paste0("Count of ", survey_question_title, " (IP:", ip, ", Phone:", phone, ")")) +
        # count of language frequency 
        geom_text(aes(label = count,
                      fontface = "bold"),
                  size = 3,
                  position = position_dodge(width = 0.9),
                  hjust = .5,
                  vjust = -0.4,
                  color = "grey40") +
        # customs
        scale_fill_manual(values = colors) +
        theme_classic()  +
        theme(
          plot.title = element_text(size = 15,
                                    hjust = .5),
          plot.subtitle = element_text(size = 12,
                                       hjust = .5),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)) # Adjust y-axis title position
        ) 
      
      # Save plot as a png
      plot_filename <- paste0(folder_path, "/", country, "/", round_of_surveying, "/", "dup_data_vis","/", "repeat_ip_cell","/",survey_question, "/", country, "_", survey_question, "duplicates_response_analysis_", round_of_surveying, "_IP_", ip, "_Phone_", phone, ".png")
      ggsave(filename = plot_filename, plot = plot_data, width = 8, height = 5, dpi = 300)
      
      print(paste("Plot for IP:", ip, "and Phone:", phone, "saved successfully."))
    }
  } else {
    print("Specified survey question column does not exist in the dataframe.")
  }
}
```

```{r}
generate_dup_plots(ind_duplicates, "IND", "stay_residence", "R1")
# not working
# stay_residence 
# flood_close 
# property_loss 
# housing_damage

```

# Lanuage Distribution

```{r fig.width=10, fig.height=6, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Grouped
plot_data_bgd %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, q_language)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, q_language) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = q_language, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Qualtrics Language Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Qualtric Detected Languages") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()
 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, q_language)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, q_language) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = q_language, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Qualtrics Language Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Qualtric Detected Languages") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()
```

# Income Brackets

```{r fig.width=12, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plotting the 5 income brackets
plot_data_bgd %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, income_brackets)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, income_brackets) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  # create histogram
  ggplot(aes(fill = gender,
             y = income_brackets,
             x = age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Income Bracket Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Tax Brackets") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -1,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plotting the 5 income brackets
plot_data_ind %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, income_brackets)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, income_brackets) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  # create histogram
  ggplot(aes(fill = gender,
             y = income_brackets,
             x = age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Income Bracket Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Tax Brackets") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -1,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Household Move

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, household_move)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, household_move) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = household_move, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Household Move Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, household_move)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, household_move) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = household_move, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Household Move Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Flood Year

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_year)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_year) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_year, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Year Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_year)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_year) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_year, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Year Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Stay Residence

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, stay_residence)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, stay_residence) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = stay_residence, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Stay Residence Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----       India           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, stay_residence)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, stay_residence) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = stay_residence, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Stay Residence Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Flood Close

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_close)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_close) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_close, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Close Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_close)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_close) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_close, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Close Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Move Rural Urban

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, move_rural_urban)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, move_rural_urban) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = move_rural_urban, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Move Rural Urban Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, move_rural_urban)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, move_rural_urban) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = move_rural_urban, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Move Rural Urban Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Property Loss

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, property_loss)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, property_loss) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = property_loss, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Property Loss Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, property_loss)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, property_loss) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = property_loss, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Property Loss Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Housing Damage

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, housing_damage)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, housing_damage) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = housing_damage, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Housing Damage Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, housing_damage)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, housing_damage) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = housing_damage, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Housing Damage Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Flood Prepared

```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_prepared)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_prepared) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_prepared, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Prepared Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_prepared)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_prepared) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_prepared, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Prepared Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  coord_flip()
```

# Contact Authority

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, contact_authority)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, contact_authority) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = contact_authority, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Contact Authority Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, contact_authority)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, contact_authority) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = contact_authority, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Contact Authority Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Enough Eat

```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, enough_eat)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, enough_eat) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = enough_eat, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Enough Eat Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, enough_eat)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, enough_eat) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = enough_eat, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Enough Eat Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Climate Problem

```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, climate_problem)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, climate_problem) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = climate_problem, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Climate Problem Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) +
  
  coord_flip()
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, climate_problem)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, climate_problem) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = climate_problem, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Climate Problem Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
```

# Trust Government

```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, trust_government)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, trust_government) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = trust_government, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Trust Government Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, trust_government)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, trust_government) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = trust_government, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Trust Government Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
```

GROUP BY CELL PHONE NO. or show the responses from the same cell no.

# No Surverys Submitted

```{r}

```
