
```{r set_up, message=FALSE, warning=FALSE}
library(sf)
library(here)
library(tmap)
library(terra)
library(stars)
library(leaflet)
#library(maptiles)
#library(devtools)
#library(ggspatial)
library(tmaptools)
#library(patchwork)
#library(sfheaders)
library(tidyverse)
#library(osmextract)
#library(tidygeocoder)
library(RColorBrewer)

set.seed(99)
```

## Raw Response Data
BGD raw = 4699
IND raw = 8554
```{r raw_responses}
# read in data
bgd_file <- file.path(here("..","data","adapt_observ_survey_responses", "Observatory_Bangladesh_2024_04_15.csv"))
  
ind_file <- file.path(here("..","data","adapt_observ_survey_responses", "Observatory_India_2024_04_15.csv"))

bgd_raw <- read_csv(bgd_file, show_col_types = FALSE)
  
ind_raw <-read_csv(ind_file, show_col_types = FALSE)

#bgd_raw_sf <- bgd_raw %>% 
 # janitor::clean_names() %>% 
  #filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
  #st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326", na.rm = TRUE) %>% 
  #st_make_valid()

#ind_raw_sf <- ind_raw %>% 
 # filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
#  st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326") %>% 
#  st_make_valid()
```

```{r target_points, message=FALSE, warning=FALSE}
# Load in Border Shapefiles
bgd_borders <- st_read(here("geospatial/country_shapefiles/geoBoundaries-BGD-ADM0-all/geoBoundaries-BGD-ADM0_simplified.shp"))

ind_borders <- st_read(here("geospatial/country_shapefiles/geoBoundaries-IND-ADM0-all/geoBoundaries-IND-ADM0_simplified.shp"))

# Import Facebook Point Targeting Data
bgd_fb <- read.csv(here("geospatial/surveying_points/bgd_survey_strat_points_1km_95th.csv"))

ind_fb <- read.csv(here("geospatial/surveying_points/ind_survey_strat_points_1km_95th.csv"))

# Buffered target points 1 km
bgd_fb_sf <- st_as_sf(bgd_fb, coords = c("X", "Y"), crs = 4326)
bgd_fb_sf_buffered <- st_buffer(bgd_fb_sf, dist = units::set_units(1000, "m"))

ind_fb_sf <- st_as_sf(ind_fb, coords = c("X", "Y"), crs = 4326)
ind_fb_sf_buffered <- st_buffer(ind_fb_sf, dist = units::set_units(1000, "m"))
```

## Potential Panelist Data
BGD cleaned = 930
IND cleaned = 495
```{r panelist_data, message=FALSE, warning=FALSE}
# load BGD data 
bgd <- read_csv("../results/clean_data/adaptation_observatory_bgd_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)  %>% 
  filter(complete.cases(location_longitude, location_latitude)) 
  


# load IND data 
ind <- read_csv("../results/clean_data/adaptation_observatory_ind_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE) %>% 
  filter(complete.cases(location_longitude, location_latitude)) 


# ---- sf objects qualtrics location ----
# create sf objects
bgd_sf <- bgd %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid()


ind_sf <- ind %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))


# ---  sf objects browser location ----
bgd_sf_browser <- bgd %>% 
  filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
  st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326") %>% 
  st_make_valid()


ind_sf_browser <- ind %>% 
  filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
  st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326") %>% 
  st_make_valid()


# Drop respondent locations outside of country boundaries
bgd_sf_intersect <- st_intersection(bgd_sf, bgd_borders)
bgd_sf_browser_intersect <- st_intersection(bgd_sf_browser, bgd_borders)

ind_sf_intersect <- st_intersection(ind_sf, ind_borders)
ind_sf_browser_intersect <- st_intersection(ind_sf_browser, ind_borders)
```

## Survey Location Accuracy 

cleaned browser locations in country / total respondents

BGD = 19.8%+≠
IND = 5.9%
```{r survey_accuracy}
# cleaned browser locations in country / total respondents
bgd_accuracy <-  nrow(bgd_sf_browser_intersect) / nrow(bgd_raw)* 100


# cleaned browser locations in country 
bin_accuracy <-  nrow(ind_sf_browser_intersect) / nrow(ind_raw)* 100
```

## KNN - needs some attention 
**Pending updates upon touching base w/ Mark**
I think bc the ad is buffered by 1 km, I need to at 1 km to all distances for this to be accurate

- Assigned unique stratum_id to all fb ads
- Using knn, assigned panelist browser location to appropriate ad stratum_id 
- Calculated the avg distance from ad location for each stratum_id
- Used these avg in histogram to see avg distance distribution across all ads
- Calculated the % of unique ad id's that were assigned to panelist browser , displayed as "Ad Success Rate"
- All distances were less than 0.5 km for BGD
- All distances were less than 2 km for IND 

The ad success rates:

BGD: 306/855 * 100 = 35.79 % of the respondents were within a 1 km distance

IND: 184/850 * 100 = 19.37 % of the respondents were within a 2 km distance


Follow up question I want to tackle over the weekend: on avg, how many responses per ad?

I want a break down of the number of responses for each stratum_id
```{r bgd_knn}
library(dplyr)
library(nngeo)

# Add identifiers back to the buffered Facebook ad data
bgd_fb_sf_buffered <- bgd_fb_sf_buffered %>%
  mutate(stratum_id = row_number())

bgd_fb_sf_buffered

# Assuming bgd_sf_browser_intersect and bgd_fb_sf_buffered are your sf objects

# Assign a unique stratum ID to each buffered ad zone
bgd_fb_sf_buffered <- bgd_fb_sf_buffered %>%
  mutate(stratum_id = row_number())

#~~~~~~~~~~~~~~~~~~~~~~~~~
#    MARK FOR INPUT
#~~~~~~~~~~~~~~~~~~~~~~~~~
# ---- knn assignment of stratum_id for ads ----
# Find the nearest buffered Facebook ad zone for each browser location using KNN

# these are 1 km buffered points, therefore, I believe the assumptions below may need adjustments
# I think I need to adjust all of the distances in the histogram by +1 km
# To get a more accurate calculation of distance

nearest_ad <- st_nn(bgd_sf_browser_intersect, bgd_fb_sf_buffered)

length(unique(nearest_ad))
```
```{r knn_check}
#head(nearest_ad, 6)
```

```{r bgd_join}
# Join the browser locations with the nearest ad zones
browser_with_ad <- bgd_sf_browser_intersect %>%
  mutate(stratum_id = nearest_ad) %>%
  # extract list contents
  unnest(cols = stratum_id)
  

head(browser_with_ad, 5)
colnames(browser_with_ad)


# how many unique ad ids are represented here?
# aka how successful were our 855 ads?
# okay 306, not great, but not 0.
length(unique(browser_with_ad$stratum_id))
```

```{r}
plot(browser_with_ad, col = browser_with_ad$stratum_id)
```

BGD ad success rate 35.8%
```{r bgd_ad_success}
# our sucess rate here was 35.8
# unique ad ids that were assigned / total number of ads deployed
ad_success_rate_bgd <- as.numeric(length(unique(browser_with_ad$stratum_id))) / as.numeric(length(bgd_fb_sf_buffered$stratum_id)) * 100

as.numeric(length(unique(browser_with_ad$stratum_id)))

as.numeric(length(bgd_fb_sf_buffered$stratum_id))
```


```{r bgd_check}
# Check if any browser locations did not get assigned a stratum ID
unassigned <- browser_with_ad[is.na(browser_with_ad$stratum_id), ]

# If there are unassigned browser locations, handle them accordingly
if (nrow(unassigned) > 0) {
  # You can choose to assign a default stratum ID or handle them in another way
  # For example:
  browser_with_ad <- bind_rows(browser_with_ad, mutate(unassigned, stratum_id = NA))
}

unassigned
# Now, every browser location should have a corresponding stratum ID
```

## Distance from Ads for Cleaned Browser Locations

1. Adjust to mutate just for each distance and make hist for all distance distrib. 

2. Facebook sampling points selected using the hpd+flood aoi : calculate the distance to the nearest point that is in that layer [mask + st_distance]
(Accuracy )
```{r bgd_dist}
# ---- distance calc for each ad strata ---- 
# Calculate distance for each stratum_id group
distance_table_bgd <- browser_with_ad %>%
  # for histogram, don't group,
  # don't summarize
  # just histogram
  
  
#  group_by(stratum_id) %>%
  # count how many responses per ad?
 # summarize(#num_responses = n_distinct(response_id),
            # calculate Mean distance in kilometers for each ad strata
          # distance_km = mean(
  mutate(distance_km = sf::st_distance(geometry, bgd_fb_sf_buffered), na.rm = TRUE) / 1000) %>% 
  mutate(distance_km = units::set_units(distance_km, "km")) 

nrow(distance_table_bgd)

distance_table_bgd

# Calculate the maximum distance
max_distance_bgd <- max(distance_table_bgd$distance_km)

max_distance_bgd
```




```{r bgd_hist}
# Define breaks for binning
breaks <- c(0, 0.3, 0.5, 1)

# Create labels for the bins
labels <- c("0-0.3 km","0.3-0.5 km", "0.5-1 km")

# Cut the distances into bins
distance_table <- distance_table %>%
  mutate(distance_bin = cut(distance_km, breaks = breaks, labels = labels, include.lowest = TRUE))

# Create the histogram
bgd_hist <- ggplot(distance_table, aes(x = distance_bin)) +
  
  geom_bar(stat = "count", fill = "skyblue", color = "black") +
  
  labs( title = "BGD Mean Strata Distribution of Distances by Nearest Ad Location (km)",
        subtitle = "Adaptation Observatory: April 15, 2024 Responses",
        x = "Distance Range (km)",
        y = "Frequency Count") +
  
  theme_minimal() +
  
  theme(
    plot.title = element_text(size = 15,
                              hjust = 0.5),
    
    plot.subtitle = element_text(size = 12,
                                 hjust = 0.5),
    
    axis.text.x = element_text(hjust = 1)) +
  
  geom_rect(
    aes(xmin = 2,
        xmax = 3.5, 
        ymin = 75, 
        ymax = 125),
    fill = "grey90",
    color = "black",
    size = 0.5,
    inherit.aes = FALSE,
    alpha = 0.1
  ) +
  # Add annotation
  annotate(
    "text",
    x = 2.75, 
    y = 85, 
    label = paste0("Maximum distance is ", round(max_distance_bgd, 3), " (km)"),
    hjust = 0.5,
    vjust = -1,
    color = "black",
    size = 5
  ) +
  geom_curve(
    aes(x = 2, y = 100, xend = 2, yend = 10),
    curvature = 0.3,
    color = "black",
    arrow = arrow(length = unit(0.3, "cm"))
  ) +
  geom_text(
    x = 2.75, 
    y = 150, 
    label = paste0("Ad Success Rate: ", round(ad_success_rate, 2), "%"),
    hjust = 0.5,
    vjust = -1,
    color = "black",
    size = 6
  )

bgd_hist

ggsave(here("response_analysis/results/response_visuals/BGD/R1/clean_data_vis/bgd_R1_targeting_dist_hist.png"), plot = bgd_hist, width = 10, height = 7, dpi = 300, bg = "white")
```

```{r ind_ad_strata_dist}
# Add identifiers back to the buffered Facebook ad data
ind_fb_sf_buffered <- ind_fb_sf_buffered %>%
  mutate(stratum_id = row_number())

#ind_fb_sf_buffered

# Assuming bgd_sf_browser_intersect and bgd_fb_sf_buffered are your sf objects

# Assign a unique stratum ID to each buffered ad zone
ind_fb_sf_buffered <- ind_fb_sf_buffered %>%
  mutate(stratum_id = row_number())

# ---- knn assignment of stratum_id for ads ----
# Find the nearest buffered Facebook ad zone for each browser location using KNN
nearest_ad_ind <- st_nn(ind_sf_browser_intersect, ind_fb_sf_buffered)

#length(unique(nearest_ad))

# Join the browser locations with the nearest ad zones
browser_with_ad_ind <- ind_sf_browser_intersect %>%
  mutate(stratum_id = nearest_ad_ind) %>%
  # extract list contents
  unnest(cols = stratum_id)
  

head(browser_with_ad_ind, 5)


# how many unique ad ids are represented here?
# aka how successful were our 950 ads?
# okay 184, not great, but not 0.
length(unique(browser_with_ad_ind$stratum_id))
# our sucess rate here was 19.4
ad_success_rate_ind <- as.numeric(length(unique(browser_with_ad_ind$stratum_id))) / as.numeric(length(ind_fb_sf_buffered$stratum_id)) * 100

# Check if any browser locations did not get assigned a stratum ID
unassigned_ind <- browser_with_ad_ind[is.na(browser_with_ad_ind$stratum_id), ]

# If there are unassigned browser locations, handle them accordingly
if (nrow(unassigned) > 0) {
  # You can choose to assign a default stratum ID or handle them in another way
  # For example:
  browser_with_ad_ind <- bind_rows(browser_with_ad_ind, mutate(unassigned, stratum_id = NA))
}

unassigned_ind
# Now, every browser location should have a corresponding stratum ID

# ---- distance calc for each ad strata ---- 
# Calculate distance for each stratum_id group
distance_table_ind <- browser_with_ad_ind %>%
  group_by(stratum_id) %>%
  # count how many responses per ad?
  summarize(num_responses = n_distinct(response_id),
            # Mean distance in kilometers for each ad strata
            distance_km = mean(sf::st_distance(geometry, ind_fb_sf_buffered), na.rm = TRUE) / 1000) %>% 
  mutate(distance_km = units::set_units(distance_km, "km")) 



nrow(distance_table_ind)

distance_table_ind


# Calculate the maximum distance
max_distance_ind <- max(distance_table_ind$distance_km)
max_distance_ind
```


```{r ind_hist}
# Define breaks for binning
breaks <- c(0, 0.3, 0.5, 1, 1.5, 2)

# Create labels for the bins
labels <- c("0-0.3 km","0.3-0.5 km", "0.5-1.0 km", "1.0-1.5 km", "1.5-2 km")

# Cut the distances into bins
distance_table_ind <- distance_table_ind %>%
  mutate(distance_bin = cut(distance_km, breaks = breaks, labels = labels, include.lowest = TRUE))

# Create the histogram
ind_hist <- ggplot(distance_table_ind, aes(x = distance_bin)) +
  
  geom_bar(stat = "count", fill = "skyblue", color = "black") +
  
  labs( title = "IND Mean Strata Distribution of Distances by Nearest Ad (km)",
        subtitle = "Adaptation Observatory: April 15, 2024 Responses",
        x = "Distance Range (km)",
        y = "Frequency Count") +
  
  theme_minimal() +
  
  theme(
    plot.title = element_text(size = 15,
                              hjust = 0.5),
    
    plot.subtitle = element_text(size = 12,
                                 hjust = 0.5),
    
    axis.text.x = element_text(hjust = 1)) +
  
  geom_rect(
    aes(xmin = 3,
        xmax = 4.9, 
        ymin = 45, 
        ymax = 25),
    fill = "grey90",
    color = "black",
    size = 0.5,
    inherit.aes = FALSE,
    alpha = 0.1
  ) +
  # Add annotation
  annotate(
    "text",
    x = 3.95, 
    y = 29, 
    label = paste0("Maximum distance is ", round(max_distance, 2), " (km)"),
    hjust = 0.5,
    vjust = -1,
    color = "black",
    size = 5
  ) +
  geom_curve(
    aes(x = 3, y = 35, xend = 2.8, yend = 10),
    curvature = 0.3,
    color = "black",
    arrow = arrow(length = unit(0.3, "cm"))
  ) +
  geom_text(
    x = 3.95, 
    y = 55, 
    label = paste0("Ad Success Rate: ", round(ad_success_rate_ind, 2), "%"),
    hjust = 0.5,
    vjust = -1,
    color = "black",
    size = 6
  )

ind_hist

ggsave(here("response_analysis/results/response_visuals/IND/R1/clean_data_vis/ind_R1_targeting_dist_hist.png"), plot = ind_hist, width = 10, height = 7, dpi = 300, bg = "white")
```

Total Distance
**NOT READY YET**
I think bc the ad is buffered by 1 km, I need to at 1 km to all distances for this to be accurate

```{r tot_distance}
# Create a table with total distances averaged
# If you want total distances averaged, it's a bit different, here's how you can do it:
total_distance_bgd <- sum(distance_table_bgd$distance_km)
total_count_bgd <- nrow(distance_table_bgd)
average_distance_bgd <- total_distance_bgd / total_count_bgd

average_distance_table_bgd <- data.frame(total_distance = total_distance_bgd, total_count = total_count_bgd, average_distance = average_distance_bgd)


#INDIA
# Create a table with total distances averaged
# If you want total distances averaged, it's a bit different, here's how you can do it:
total_distance_ind <- sum(distance_table_ind$distance_km)
total_count_ind <- nrow(distance_table_ind)
average_distance_ind <- total_distance_ind / total_count_ind

average_distance_table_ind <- data.frame(total_distance = total_distance_ind, total_count = total_count_ind, average_distance = average_distance_ind)

average_distance_table_ind
```