---
<!DOCTYPE html>
<html>

<head>
  <style>
    .chart {
      width: 100%;
      height: 500px;
    }
  </style>
</head>

<body>
  <div class="chart-sunburst chart"></div>
</body>

<script src="../index.js"></script>

</html>
---

# Sunburst Plot

Broken up by region
- inside each region: 
  - what are the gender percentages?:
    - within those, what are:
        - age, demo_age:
               # impact of floods
              - flood_year, housing_damage, property_loss, contact_authority, flood_close,
               # socioeconomic factors & resiliency / scarcity 
              - stay_residence, flood_prepared, housing_safe, enough_eat, move_rural_urban, demo_income, 
               # sentiments 
              - climate_problem, trust_government
              
For simplicities sake, let's make a series of these:

- Region: Gender: Age

- Region: Gender: Demo_Gender: Age: 
- Region: Gender: Age: Demo_Age:

- Region: Gender: Demo_Gender: Age: Demo_Age:


- Region: Gender: Age: {insert variables, e.g. flood_year}: 
## Set up
```{r message = FALSE}
library(tidyverse)
library(here)
library(d3r)
library(sunburstR)
library(htmltools)
library(htmlwidgets)
```


## Load & Wrangle Survey Demographic Data
```{r warning = FALSE}
# load function
# Source the .R file containing the function
source(here("survey_responses/read_n_wrangle_data.R"))

bgd_responses <- file.path(here("..","..","data","adapt_observ_survey_responses", "Observatory_Bangladesh_2024_04_15.csv"))
  
ind_responses <- file.path(here("..","..","data","adapt_observ_survey_responses", "Observatory_India_2024_04_15.csv"))


bgd_demos <- read.csv(bgd_responses, package="sunburstR", stringsAsFactors = FALSE)
ind_demos <- read.csv(ind_responses, stringsAsFactors = FALSE)

#bgd_demos <-read_n_wrangle_data(bgd_responses)
bgd_demos

ind_demos <- read.csv("../../data/adapt_observ_survey_responses/Observatory_India_2024_04_15.csv", stringsAsFactors = FALSE)
bgd_demos <- read.csv("../../data/adapt_observ_survey_responses/Observatory_Bangladesh_2024_04_15.csv", stringsAsFactors = FALSE)

ind_demos <- read.csv(system.file("../../data/adapt_observ_survey_responses/Observatory_India_2024_04_15.csv", package = "sunburstR"), stringsAsFactors = FALSE)

#ind_demos <- read_n_wrangle_data(ind_responses)
ind_demos <- read.csv(system.file("../../data/adapt_observ_survey_responses/Observatory_India_2024_04_15.csv", package="sunburstR"), stringsAsFactors = FALSE)

bgd_demos <- read.csv(system.file(bgd_responses, package = "sunburstR"), stringsAsFactors = FALSE)

ind_demos
```

## Subset duplicate ip_addresses
```{r multiple_responses}
# let's filter ip address that have responded more than once
# 1031 ip addressses appeared more than once
repeated_ip_addr <- bgd_demos %>%
  group_by(ip_address) %>%
  filter(n() > 1)

repeated_ip_addr

# now let's collect the different responses of those ip addresses
# we expect a many to many relationship between these df 
# 3957 responses were pulled from the repeating ip addr
#multiple_responses <- semi_join(bgd_demos, repeated_ip_addr, by = "ip_address") 

multiple_responses <- inner_join(bgd_demos, repeated_ip_addr, by = "ip_address") 


# Select columns to pivot (excluding ip_address)
cols_to_pivot <- setdiff(names(multiple_responses), "ip_address")

# Pivot selected columns into long format
multiple_responses <- multiple_responses %>%
  # clean funky column outputs bc we only want to join by ip_address 
  pivot_longer(cols = all_of(cols_to_pivot), 
               # store x and y in a new column called variable
               names_to = c(".value", "variable"), 
               # use the . in the colname to separate unwanted the characters 
               names_sep = "\\.") %>% 
  # remove duplicate entrees that were created using pivot_longer()
  filter(!grepl("y", variable)) %>% 
  # remove extra column
  dplyr::select(-'variable')

multiple_responses
```
```{r multi_rep_percs}
# Columns to calculate percentages for Yes or No responses
# things commented out are on a scale - will display those using a bar plot
cols_to_calc <- c("flood_year", "housing_damage", "property_loss", "contact_authority",
                  "flood_close", "stay_residence", 
                  "enough_eat", "move_rural_urban")

multi_rep_percs <- multiple_responses %>% 
  
  # Treat NA as a separate category
  mutate(across(where(is.character), ~ifelse(. %in% c(NA, "NA"), "Not Disclosed", .)),
         across(where(is.numeric), ~ifelse(is.na(.), "Not Disclosed", .))) %>% 
  
  mutate(path = paste(region, gender, age, sep="-")) %>%
  
  group_by(path) %>% 

  mutate(
    across(
      .cols = all_of(cols_to_calc),
      .fns = list(
        Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
        No = ~ (sum(. == "No" | . == "no") / n()),
        `Not Disclosed` = ~ (sum(. == "Not Disclosed") / n())
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
    dplyr::select(path, ends_with("_Yes"), ends_with("_No"), ends_with("_Not Disclosed"))
  
  
```


```{r}
tree <- d3_nest(multi_rep_percs)
str(tree)

sb1 <- sunburst(tree, width="100%", height=400)
sb1
```

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(sunburstR)

# Assuming `multi_rep_percs` is your original data frame

# Pivot the data frame to long format
multi_rep_percs_long <- multi_rep_percs %>%
  pivot_longer(cols = -path, names_to = "category", values_to = "value")

# Split the path column into individual components
multi_rep_percs_long <- multi_rep_percs_long %>%
  separate(path, into = c("level1", "level2", "level3"), sep = "-", remove = FALSE)

# Create a hierarchical structure for sunburstR
hierarchical_data <- multi_rep_percs_long %>%
  group_by(level1, level2, level3) %>%
  summarise(value = sum(value), .groups = "drop") %>%
  ungroup() %>%
  mutate_all(as.character) %>%
  mutate(
    name = paste(level1, level2, level3, sep = "-"),
    path = paste(level1, level2, level3, sep = "-")
  ) %>%
  select(path, name, value)

# Convert the hierarchical data to JSON format
json_data <- toJSON(hierarchical_data, pretty = TRUE)

# Now `json_data` contains the adapted hierarchical data in JSON format,
# which we can use with the `sunburst()` function in the `sunburstR` package.
# Create the sunburst plot using  hierarchical data
sunburst_plot <- sunburst(json_data, width = "100%", height = 400)

sunburst_plot
```


```{r}
# Assuming tree contains JSON data

# Create a sunburst chart using the JSON data
sb1 <- htmltools::htmlDependency(
  "d3_sunburst", "2.0.0", 
  src = c(href = "https://d3js.org"), 
  script = "d3.v2.min.js"
)

htmltools::tagList(
  tags$head(
    tags$script(src = "https://d3js.org/d3.v2.min.js"),
    sb1
  ),
  tags$body(
    tags$div(id = "sunburst-chart")
  ),
  tags$script(HTML(sprintf("
    var treeData = %s;
    var width = 750;
    var height = 600;
    var radius = Math.min(width, height) / 2;
    var color = d3.scale.category20c();

    var svg = d3.select('#sunburst-chart').append('svg')
      .attr('width', width)
      .attr('height', height)
      .append('g')
      .attr('transform', 'translate(' + width / 2 + ',' + height / 2 + ')');

    var partition = d3.layout.partition()
      .sort(null)
      .size([2 * Math.PI, radius * radius])
      .value(function(d) { return d.size; });

    var arc = d3.svg.arc()
      .startAngle(function(d) { return d.x; })
      .endAngle(function(d) { return d.x + d.dx; })
      .innerRadius(function(d) { return Math.sqrt(d.y); })
      .outerRadius(function(d) { return Math.sqrt(d.y + d.dy); });

    var path = svg.selectAll('path')
      .data(partition.nodes(treeData))
      .enter().append('path')
      .attr('display', function(d) { return d.depth ? null : 'none'; }) // hide inner ring
      .attr('d', arc)
      .style('stroke', '#fff')
      .style('fill', function(d) { return color((d.children ? d : d.parent).name); })
      .style('fill-rule', 'evenodd')
      .each(stash);

    function stash(d) {
      d.x0 = d.x;
      d.dx0 = d.dx;
    }

    // Interpolate the scales!
    function arcTween(a) {
      var i = d3.interpolate({x: a.x0, dx: a.dx0}, a);
      return function(t) {
        var b = i(t);
        a.x0 = b.x;
        a.dx0 = b.dx;
        return arc(b);
      };
    }

    d3.select(self.frameElement).style('height', height + 'px');
  ", tree))
)
)

```


```{r}

# Plot
flood_year_burst <- sunburst(multi_rep_percs, legend=FALSE)

flood_year_burst
```


```{r}
multi_rep_percs <- multiple_responses %>% 
  
  # Treat NA as a separate category
  mutate(across(where(is.character), ~ifelse(. %in% c(NA, "NA"), "Not Disclosed", .)),
         across(where(is.numeric), ~ifelse(is.na(.), "Not Disclosed", .))) %>% 
  
  # Convert to factor
  mutate_at(vars(flood_year),
            ~factor(., levels = c("Yes", "No", "Not Disclosed"), exclude = NULL)) %>% 
  
    
  mutate(path = paste(region, gender, demo_gender, age, demo_age, sep="-")) %>%
  
  group_by(path) %>% 

  mutate(
    across(
      .cols = all_of(cols_to_calc),
      .fns = list(
        Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
        No = ~ (sum(. == "No" | . == "no") / n()),
        `Not Disclosed` = ~ (sum(. == "Not Disclosed") / n())
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
    dplyr::select(path, ends_with("_Yes"), ends_with("_No"), ends_with("_Not Disclosed"))
  
  
#colnames(multi_rep_percs)
#multi_rep_percs

# Plot
flood_year_demo_burst <- sunburst(multi_rep_percs, legend=FALSE)

flood_year_demo_burst
```



--- sdb
```{r}
# Group the data by region, gender, and age
grouped_data <- multi_rep_percs %>%
  separate(path, into = c("region", "gender", "age"), sep = "-") %>%
  group_by(region, gender, age) %>%
  summarise_all(list(mean))

#summary(grouped_data)
# Create the tree structure
tree <- d3_nest(grouped_data)

# Create the sunburst plot
sb <- sund2b(tree, width = "100%")

# Display the plot
div(
  style = "display: flex; align-items:center;",
  sb
)
```


```{r sunburst_tut}
library(htmltools)
library(d3r)

# Group the data by region, gender, and age
grouped_data <- multi_rep_percs %>%
  separate(path, into = c("region", "gender", "age"), sep = "-") %>%
  group_by(region, gender, age) %>%
  summarise_all(list(mean))

grouped_data

tree <- d3_nest(grouped_data)
tree

sb3 <- sund2b(tree, width="100%")

div(
  style="display: flex; align-items:center;",
  sb3
)
```



```{r personal_demo}
multi_rep_percs <- multiple_responses %>% 
  
  # Treat NA as a separate category
  mutate(across(where(is.character), ~ifelse(. %in% c(NA, "NA"), "Not Disclosed", .)),
         across(where(is.numeric), ~ifelse(is.na(.), "Not Disclosed", .))) %>% 
  
  # Convert to factor
 # mutate_at(vars(flood_year, housing_damage, property_loss, contact_authority, flood_close,
 #                 stay_residence, flood_prepared, housing_safe, enough_eat, move_rural_urban,
  #                demo_income, climate_problem, trust_government),
   #         ~factor(., levels = c("Yes", "No", "Not Shared"), exclude = NULL)) %>% 
  
    
  mutate(path = paste(region, gender, demo_gender, sep="-")) %>%
  
  group_by(path, age)# %>% 

 # mutate(
  #  across(
   #   .cols = all_of(cols_to_calc),
    #  .fns = list(
     #   Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
      #  No = ~ (sum(. == "No" | . == "no") / n()),
       # `Not Shared` = ~ (sum(. == "Not Shared") / n())
    #  ),
    #  .names = "{.col}_{.fn}"
  #  )
  #) %>% 

  mutate(
    age_groups <- 
    
    across(
      .cols = age,
      .fns = list(
        Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
        No = ~ (sum(. == "No" | . == "no") / n()),
        `Not Shared` = ~ (sum(. == "Not Shared") / n())
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
    dplyr::select(path, ends_with("_Yes"), ends_with("_No"), ends_with("_Not Shared"))
  
  
colnames(multi_rep_percs)
multi_rep_percs

# Plot
p <- sunburst(multi_rep_percs, legend=FALSE)
p
```


```{r sunburst_demographics}
# Columns to calculate percentages for Yes or No responses
# things commented out are on a scale - will display those using a bar plot
cols_to_calc <- c("flood_year", "housing_damage", "property_loss", "contact_authority",
                  "flood_close", "stay_residence", 
                  #"flood_prepared", "housing_safe",
                  "enough_eat", "move_rural_urban"#, 
                  #"demo_income", "climate_problem", 
                 # "trust_government"
                 )


multi_rep_percs <- multiple_responses %>% 
  
  # Treat NA as a separate category
  mutate(across(where(is.character), ~ifelse(. %in% c(NA, "NA"), "Not Disclosed", .)),
         across(where(is.numeric), ~ifelse(is.na(.), "Not Disclosed", .))) %>% 
  
  # Convert to factor
  mutate_at(vars(flood_year, housing_damage, property_loss, contact_authority, flood_close,
                  stay_residence, flood_prepared, housing_safe, enough_eat, move_rural_urban,
                  demo_income, climate_problem, trust_government),
            ~factor(., levels = c("Yes", "No", "Not Disclosed"), exclude = NULL)) %>% 
  
    
  mutate(path = paste(region, gender, age, sep="-")) %>%
  
  group_by(path) %>% 

  mutate(
    across(
      .cols = all_of(cols_to_calc),
      .fns = list(
        Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
        No = ~ (sum(. == "No" | . == "no") / n()),
        `Not Disclosed` = ~ (sum(. == "Not Disclosed") / n())
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
    dplyr::select(path, ends_with("_Yes"), ends_with("_No"), ends_with("_Not Disclosed"))
  
  
colnames(multi_rep_percs)
multi_rep_percs
#str(multi_rep_percs)

# Plot
p <- sunburst(multi_rep_percs, legend=FALSE)

p
```



# This is the most complex version
The subsections need titles so it's more intuitive 

```{r full_sunburst_wo_hovertag}
# Columns to calculate percentages for Yes or No responses
# things commented out are on a scale - will display those using a bar plot
cols_to_calc <- c("flood_year", "housing_damage", "property_loss", "contact_authority",
                  "flood_close", "stay_residence", 
                  #"flood_prepared", "housing_safe",
                  "enough_eat", "move_rural_urban"#, 
                  #"demo_income", "climate_problem", 
                 # "trust_government"
                 )


multi_rep_percs <- multiple_responses %>% 
  
  # Treat NA as a separate category
  mutate(across(where(is.character), ~ifelse(. %in% c(NA, "NA"), "Not Disclosed", .)),
         across(where(is.numeric), ~ifelse(is.na(.), "Not Disclosed", .))) %>% 
  
  # Convert to factor
  mutate_at(vars(flood_year, housing_damage, property_loss, contact_authority, flood_close,
                  stay_residence, enough_eat, move_rural_urban),
            ~factor(., levels = c("Yes", "No", "Not Disclosed"), exclude = NULL)) %>% 
  
    
  mutate(path = paste(region, gender, demo_gender, age, demo_age, sep="-")) %>%
  
  group_by(path) %>% 

  mutate(
    across(
      .cols = all_of(cols_to_calc),
      .fns = list(
        Yes = ~ (sum(. == "Yes" | . == "yes") / n()),
        No = ~ (sum(. == "No" | . == "no") / n()),
        `Not Disclosed` = ~ (sum(. == "Not Disclosed") / n())
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
    dplyr::select(path, ends_with("_Yes"), ends_with("_No"), ends_with("_Not Disclosed"))
  
  
#colnames(multi_rep_percs)
#multi_rep_percs

# Plot
p <- sunburst(multi_rep_percs, legend=FALSE)

p
```
