---
title: "Descriptive Demographic Response Distributions"
author: "Sofia Ingersoll"
output:
  html-document:
    code_folding: show
    toc: true
    toc_float: true
---
# Adaptation Observatory Responses
## India & Bangladesh
### 2024 April 15

#### Overview & Goals 
- Visuals of the response distributions from each demo. group
- Visualizing the difference in the responses from those duplicates

- Isolate quality respondents, their locations and the boundary of cell tower locations

- Break down of each topic, then note the ones with the greatest variation

- i should create break downs of each demogs, responses as it’s own histogram

- so function to sort by gender and age, then display other things

- also have one just for gender age + demo gender age


#### Set up
```{r}
library(here)
library(tidyverse)
library(RColorBrewer)
```



```{r}
# load BGD data 
bgd <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
bgd_dup <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE)


# load IND data 
ind <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
ind_dup <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE)
```


IDEAS
```{r}
colnames(ind)
```


GROUP BY AGE & GENDER: DISPLAY COUNT OF ANSWER 
subset data or select group

x = answer
y = count

GROUPING BY GENDER AND AGE GROUPS

Age groups:
age >= 18 & age < 30
age >= 30 & age < 50
age >= 50 

color = gender

#### BGD
```{r}
# data wrangling
plot_data_bgd <- bgd %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(age_group, gender, demo_gender, demo_age, age,
         q_language, income_brackets, demo_income,
         household_move, flood_year, stay_residence,
         flood_close, move_rural_urban, property_loss,
         housing_damage, flood_prepared, contact_authority,
         enough_eat, climate_problem, trust_government,
         no_surverys_submitted) 

plot_data_bgd
```

#### IND 
```{r}
# data wrangling
plot_data_ind <- ind %>%  
  mutate(age_group = case_when(
    (age >= 18 & age < 30) ~ "18-29",
    (age >= 30 & age < 50) ~ "30-49",
    (age >= 50) ~ "50+"
   )) %>% 
  mutate(age = as.integer(age)) %>% 
  filter(!is.na(age)) %>% 
  dplyr::select(age_group, gender, demo_gender, demo_age, age,
         q_language, income_brackets, demo_income,
         household_move, flood_year, stay_residence,
         flood_close, move_rural_urban, property_loss,
         housing_damage, flood_prepared, contact_authority,
         enough_eat, climate_problem, trust_government,
         no_surverys_submitted) 

plot_data_ind
```

# Set up
```{r}
colors <- c("Female" = "#D16014", "Male" = "#17255A")
#"#C4A287"
```

# Lanuage Distribution 
```{r fig.width=10, fig.height=6, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Grouped
plot_data_bgd %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, q_language)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, q_language) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = q_language, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Qualtrics Language Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Qualtric Detected Languages") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()
 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, q_language)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, q_language) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = q_language, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Qualtrics Language Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Qualtric Detected Languages") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()
```

# Income Brackets 
```{r fig.width=12, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plotting the 5 income brackets
plot_data_bgd %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, income_brackets)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, income_brackets) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  # create histogram
  ggplot(aes(fill = gender,
             y = income_brackets,
             x = age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Income Bracket Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Tax Brackets") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -1,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plotting the 5 income brackets
plot_data_ind %>%
    # label groups by age demo
  mutate(age_group = fct_reorder(age_group, income_brackets)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, income_brackets) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  # create histogram
  ggplot(aes(fill = gender,
             y = income_brackets,
             x = age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Income Bracket Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Tax Brackets") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -1,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Household Move
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, household_move)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, household_move) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = household_move, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Household Move Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, household_move)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, household_move) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = household_move, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Household Move Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Flood Year
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_year)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_year) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_year, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Year Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----        India          ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_year)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_year) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_year, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Year Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Stay Residence
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, stay_residence)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, stay_residence) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = stay_residence, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Stay Residence Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----       India           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, stay_residence)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, stay_residence) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = stay_residence, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Stay Residence Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Flood Close
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_close)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_close) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_close, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Close Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_close)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_close) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_close, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Close Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Move Rural Urban
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, move_rural_urban)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, move_rural_urban) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = move_rural_urban, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Move Rural Urban Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, move_rural_urban)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, move_rural_urban) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = move_rural_urban, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Move Rural Urban Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Property Loss
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, property_loss)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, property_loss) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = property_loss, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Property Loss Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, property_loss)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, property_loss) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = property_loss, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Property Loss Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
```

# Housing Damage
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, housing_damage)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, housing_damage) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = housing_damage, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Housing Damage Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, housing_damage)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, housing_damage) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = housing_damage, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Housing Damage Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Flood Prepared
```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_prepared)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_prepared) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_prepared, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Flood Prepared Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  
  coord_flip()

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, flood_prepared)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, flood_prepared) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = flood_prepared, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Flood Prepared Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  ) +
  coord_flip()
```

# Contact Authority
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, contact_authority)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, contact_authority) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = contact_authority, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Contact Authority Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, contact_authority)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, contact_authority) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = contact_authority, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Contact Authority Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Enough Eat
```{r fig.width=8, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, enough_eat)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, enough_eat) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = enough_eat, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Enough Eat Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, enough_eat)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, enough_eat) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = enough_eat, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Enough Eat Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = .5,
            vjust = -0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
    
  )
```

# Climate Problem
```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, climate_problem)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, climate_problem) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = climate_problem, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Climate Problem Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) +
  
  coord_flip()
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, climate_problem)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, climate_problem) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = climate_problem, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Climate Problem Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
```

# Trust Government
```{r fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         BGD           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_bgd %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, trust_government)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, trust_government) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = trust_government, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "BGD Trust Government Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ----         IND           ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Subset data for plotting 
plot_data_ind %>%
  # label groups by age demo
  mutate(age_group = fct_reorder(age_group, trust_government)) %>%
  mutate(age_group = factor(age_group, levels=c("18-29", "30-49", "50+"))) %>%
  
  # count frequency 
  group_by(age_group, gender, trust_government) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  
  # create histogram
  ggplot(aes(fill = gender, y = trust_government, x= age_group)) + 
  geom_col(position="dodge", alpha=0.5, outlier.colour="transparent") +
  
  labs(title = "IND Trust Government Distribution in Age Demographics",
       subtitle = "Adaptation Observatory Survey Responses: 2024 April 15",
       x = "Age Demographic Groups",
       y = "Survey Response") +
  
  # count of language frequency 
  geom_text(aes(label = count,
                fontface = "bold"),
            size = 3,
            position = position_dodge(width = 0.9),
            hjust = -1.5,
            vjust = 0.4,
            color = "grey40") +
  
  # customs
  scale_fill_manual(values = colors) +
  
  
  theme_classic()  +
  
  theme(
    plot.title = element_text(size = 15,
                         hjust = .5),
    
    plot.subtitle = element_text(size = 12,
                            hjust = .5)
  ) + 
  
  coord_flip()
```


# No Surverys Submitted
```{r}

```


GROUP BY CELL PHONE NO. or show the responses from the same cell no.
