# Map

## Load & Wrangle Survey Demographic Data
```{r message=FALSE, warning=FALSE}
library(sf)
library(here)
library(tmap)
library(terra)
library(stars)
library(leaflet)
#library(maptiles)
#library(devtools)
#library(ggspatial)
#library(tmaptools)
#library(patchwork)
#library(sfheaders)
library(tidyverse)
#library(osmextract)
#library(tidygeocoder)
#library(RColorBrewer)
```


```{r message=FALSE, warning=FALSE}
# load BGD data 
bgd <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
# group duplicated by phone & ip
bgd_dup <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE) %>% 
  group_by(comp_phone1_try1, ip_address)


# load IND data 
ind <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
# group duplicated by phone & ip
ind_dup <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE) %>% 
  group_by(comp_phone1_try1, ip_address)

# create sf objects
bgd_sf <- bgd %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))


ind_sf <- ind %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))


bgd_sf_browser <- bgd %>% 
  filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
  st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326") %>% 
  st_make_valid()


ind_sf_browser <- ind %>% 
  filter(!is.na(geo_lng) & !is.na(geo_lat)) %>%
  st_as_sf(coords = c("geo_lng", "geo_lat"), crs = "EPSG:4326") %>% 
  st_make_valid()

# for duplicates
bgd_dup_sf <- bgd_dup %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))

# for duplicates
ind_dup_sf <- ind_dup %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))
```

### Let's remove people outside our AOI
We'll do this using a st_join( .pred = st_intersects) using the shapefiles we used to generate the geo-points

```{r}
# read in the shape files
bgd_shp <- read_stars(here("../data/country_datas/bgd_pd_2020_1km.tif")) %>% 
  st_as_sf(crs = "EPSG:4326") %>% 
  st_make_valid()


ind_shp <- read_stars(here("../data/country_datas/ind_pd_2020_1km.tif")) %>% 
  st_as_sf(crs = "EPSG:4326") %>% 
  st_make_valid()
```


# Join

**Note to self, need to update clean_data with this**
```{r}
# Assuming you have a geometry column named 'geometry' in your data frames bgd and ind
# Extract the bounding box from the geometry column
bgd_bbox <- st_bbox(st_union(bgd_shp$geometry))

# Create bounding box polygons using sf
bgd_polygon <- st_as_sfc(st_bbox(bgd_bbox), crs = 4326) %>% 
  st_as_sf()

# Filter points within the AOI using st_intersection
# reduced down to 2238 from 2247
bgd_aoi <- st_intersection(bgd_sf, bgd_polygon)

# save as csv
st_write(bgd_aoi, 
         here("response_analysis/potential_panelists/bgd_ideal_survey_panelists.csv"),
         layer_options = "GEOMETRY=AS_XY")

# this takes a fat minute
ind_bbox <- st_bbox(st_union(ind_shp$geometry))

# Create bounding box polygons using sf
ind_polygon <- st_as_sfc(st_bbox(ind_bbox), crs = 4326) %>% 
  st_as_sf()

# Filter points within the AOI using st_intersection
# reduced down to 1213 from 1214
ind_aoi <- st_intersection(ind_sf, ind_polygon)

# save as csv
st_write(ind_aoi, 
         here("response_analysis/potential_panelists/ind_ideal_survey_panelists.csv"),
         layer_options = "GEOMETRY=AS_XY")
```


## Geospatial Analysis
For anoynmity purposes, it's best these plots don't render with the IP Addresses
```{r}
tmap_mode('view')

ind_response_map <- ind_aoi %>% 
  dplyr::select(-q_url) %>% 
  tm_shape()  +
  tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_bubbles(alpha = 0.2,
             fill = 'ip_address',
             col = 'skyblue',) +
  tm_scalebar(position = c('left', 'bottom')) +
  tm_title("Adaptation Observatory Responses, Bangladesh (2024-4-11)")


tmap_save(ind_response_map,
        filename = here("response_analysis/response_visuals/IND_response_visuals/ind_aoi_map.png"))

ind_response_map
```


```{r}
tmap_mode('view')

bgd_response_map <- bgd_aoi %>% 
  dplyr::select(-q_url) %>% 
  tm_shape() +
  tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_bubbles(alpha = 0.2,
             fill = 'ip_address',
             col = 'skyblue',) +
  tm_scalebar(position = c('left', 'bottom')) +
  tm_title("Adaptation Observatory Responses, Bangladesh (2024-4-11)")


tmap_save(bgd_response_map,
        filename = here("response_analysis/response_visuals/BGD_response_visuals/bgd_aoi_map.png"))

bgd_response_map
```

### What's the most number of surveys a single ip address has submitted?
```{r}
# let's check our new column
max(bgd_demos$number_of_surverys_submitted)

max(ind_demos$number_of_surverys_submitted)
```


### Simple Plot with Facebook Targeting
```{r}
# Load in Border Shapefiles
bgd_borders <- st_read("~/Documents/GitHub/Adaptation_Observatory/geospatial/country_shapefiles/geoBoundaries-BGD-ADM0-all/geoBoundaries-BGD-ADM0_simplified.shp")

ind_borders <- st_read("~/Documents/GitHub/Adaptation_Observatory/geospatial/country_shapefiles/geoBoundaries-IND-ADM0-all/geoBoundaries-IND-ADM0_simplified.shp")

# Import Facebook Point Targeting Data
bgd_fb <- read.csv("~/Documents/GitHub/Adaptation_Observatory/geospatial/surveying_points/bgd_survey_strat_points_1km_95th.csv")

ind_fb <- read.csv("~/Documents/GitHub/Adaptation_Observatory/geospatial/surveying_points/ind_survey_strat_points_1km_95th.csv")

bgd_fb_sf <- st_as_sf(bgd_fb, coords = c("X", "Y"), crs = 4326)
bgd_fb_sf_buffered <- st_buffer(bgd_fb_sf, dist = units::set_units(1000, "m"))

ind_fb_sf <- st_as_sf(ind_fb, coords = c("X", "Y"), crs = 4326)
ind_fb_sf_buffered <- st_buffer(ind_fb_sf, dist = units::set_units(1000, "m"))


# Drop respondent locations outside of country boundaries
bgd_sf_intersect <- st_intersection(bgd_sf, bgd_borders)
bgd_sf_browser_intersect <- st_intersection(bgd_sf_browser, bgd_borders)

ind_sf_intersect <- st_intersection(ind_sf, ind_borders)
ind_sf_browser_intersect <- st_intersection(ind_sf_browser, ind_borders)


bgd_plt <- ggplot() +
  geom_sf(data = bgd_sf_browser_intersect, aes(fill = "Respondents Browser Location", shape = "Respondents Browser Location"), color = "blue", size = 0.25, alpha = 0.5) + 
  geom_sf(data = bgd_sf_intersect, aes(fill = "Respondents Qualtrics Location", shape = "Respondents Qualtrics Location"), color = "skyblue", size = 0.25, alpha = 0.2) + 
  geom_sf(data = bgd_fb_sf_buffered, aes(fill = "Targeted Points", shape = "Targeted Points"), alpha = 1, color = NA) +
  geom_sf(data = bgd_borders, aes(color = "Bangladesh border", linetype = "Bangladesh border"), size = 4, fill = NA, color = "black") +
  scale_fill_manual(name = "", 
                    values = c("Targeted Points" = "red", 
                               "Respondents Browser Location" = "blue", 
                               "Respondents Qualtrics Location" = "skyblue"),
                    guide = guide_legend(order = 1, nrow = 1)) +
  scale_shape_manual(name = "", 
                     values = c("Targeted Points" = 21, 
                                "Respondents Browser Location" = 21, 
                                "Respondents Qualtrics Location" = 24),
                     guide = guide_legend(order = 1, nrow = 1)) +
  scale_linetype_manual(name = "", values = c("Bangladesh border" = "solid"),
                        guide = guide_legend(order = 2, nrow = 1)) +

  labs(
    title = "Bangladesh R1 Spatial Targeting"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom", 
    legend.box = "vertical", 
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.text = element_text(size = 9),
    legend.spacing.x = unit(0.25, 'cm'),
    legend.key.height = unit(0.1, "lines"),  # Adjust this for height of individual keys
    axis.text = element_text(color = "black") # Change axis labels to be black
  )
bgd_plt

ggsave("~/Documents/GitHub/Adaptation_Observatory/response_analysis/results/response_visuals/BGD/R1/clean_data_vis/bgd_R1_targeting_map.png", plot = bgd_plt, width = 10, height = 7, dpi = 300, bg = "white")

ind_plt <- ggplot() +
  geom_sf(data = ind_sf_browser_intersect, aes(fill = "Respondents Browser Location", shape = "Respondents Browser Location"), color = "blue", size = 0.25, alpha = 0.5) + 
  geom_sf(data = ind_sf_intersect, aes(fill = "Respondents Qualtrics Location", shape = "Respondents Qualtrics Location"), color = "skyblue", size = 0.25, alpha = 0.2) + 
  geom_sf(data = ind_fb_sf_buffered, aes(fill = "Targeted Points", shape = "Targeted Points"), alpha = 1, color = NA) +
  geom_sf(data = ind_borders, aes(color = "India border", linetype = "India border"), size = 4, fill = NA, color = "black") +
  scale_fill_manual(name = "", 
                    values = c("Targeted Points" = "red", 
                               "Respondents Browser Location" = "blue", 
                               "Respondents Qualtrics Location" = "skyblue"),
                    guide = guide_legend(order = 1, nrow = 1)) +
  scale_shape_manual(name = "", 
                     values = c("Targeted Points" = 21, 
                                "Respondents Browser Location" = 21, 
                                "Respondents Qualtrics Location" = 24),
                     guide = guide_legend(order = 1, nrow = 1)) +
  scale_linetype_manual(name = "", values = c("India border" = "solid"),
                        guide = guide_legend(order = 2, nrow = 1)) +

  labs(
    title = "India R1 Spatial Targeting"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom", 
    legend.box = "vertical", 
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.text = element_text(size = 9),
    legend.spacing.x = unit(0.25, 'cm'),
    legend.key.height = unit(0.1, "lines"),  # Adjust this for height of individual keys
    axis.text = element_text(color = "black") # Change axis labels to be black
  )
ind_plt

ggsave("~/Documents/GitHub/Adaptation_Observatory/response_analysis/results/response_visuals/IND/R1/clean_data_vis/ind_R1_targeting_map.png", plot = ind_plt, width = 10, height = 7, dpi = 300, bg = "white")

```

