# Map

## Load & Wrangle Survey Demographic Data
```{r message=FALSE, warning=FALSE}
library(sf)
library(here)
library(tmap)
library(terra)
library(stars)
library(leaflet)
library(maptiles)
library(devtools)
library(ggspatial)
library(tmaptools)
library(patchwork)
library(sfheaders)
library(tidyverse)
library(osmextract)
library(tidygeocoder)
library(RColorBrewer)
```


```{r message=FALSE, warning=FALSE}
# load BGD data 
bgd <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
bgd_dup <- read_csv("../clean_data/adaptation_observatory_bgd_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE)


# load IND data 
ind <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_survey_questions_R1.csv",
                show_col_types = FALSE)
ind_dup <- read_csv("../clean_data/adaptation_observatory_ind_cleaned_duplicate_survey_questions_R1.csv",
                    show_col_types = FALSE)

# create sf objects
bgd_sf <- bgd %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))


ind_sf <- ind %>% 
  st_as_sf(coords = c("location_longitude", "location_latitude"), crs = "EPSG:4326") %>% 
  st_make_valid() %>% 
  filter(!is.na(geometry))
```

### Let's remove people outside our AOI
We'll do this using a st_join( .pred = st_intersects) using the shapefiles we used to generate the geo-points

```{r}
# read in the shape files
bgd_shp <- read_stars(here("../data/country_datas/bgd_pd_2020_1km.tif")) %>% 
  st_as_sf(crs = "EPSG:4326") %>% 
  st_make_valid()


ind_shp <- read_stars(here("../data/country_datas/ind_pd_2020_1km.tif")) %>% 
  st_as_sf(crs = "EPSG:4326") %>% 
  st_make_valid()
```


# Join

**Note to self, need to update clean_data with this**
```{r}
# Assuming you have a geometry column named 'geometry' in your data frames bgd and ind
# Extract the bounding box from the geometry column
bgd_bbox <- st_bbox(st_union(bgd_shp$geometry))

# Create bounding box polygons using sf
bgd_polygon <- st_as_sfc(st_bbox(bgd_bbox), crs = 4326) %>% 
  st_as_sf()

# Filter points within the AOI using st_intersection
# reduced down to 2238 from 2247
bgd_aoi <- st_intersection(bgd_sf, bgd_polygon)

# save as csv
st_write(bgd_aoi, 
         here("response_analysis/potential_panelists/bgd_ideal_survey_panelists.csv"),
         layer_options = "GEOMETRY=AS_XY")

# this takes a fat minute
ind_bbox <- st_bbox(st_union(ind_shp$geometry))

# Create bounding box polygons using sf
ind_polygon <- st_as_sfc(st_bbox(ind_bbox), crs = 4326) %>% 
  st_as_sf()

# Filter points within the AOI using st_intersection
# reduced down to 1213 from 1214
ind_aoi <- st_intersection(ind_sf, ind_polygon)

# save as csv
st_write(ind_aoi, 
         here("response_analysis/potential_panelists/ind_ideal_survey_panelists.csv"),
         layer_options = "GEOMETRY=AS_XY")
```


## Geospatial Analysis
For anoynmity purposes, it's best these plots don't render with the IP Addresses
```{r}
tmap_mode('view')

ind_response_map <- ind_aoi %>% 
  dplyr::select(-q_url) %>% 
  tm_shape()  +
  tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_bubbles(alpha = 0.2,
             fill = 'ip_address',
             col = 'skyblue',) +
  tm_scalebar(position = c('left', 'bottom')) +
  tm_title("Adaptation Observatory Responses, Bangladesh (2024-4-11)")


tmap_save(ind_response_map,
        filename = here("response_analysis/response_visuals/IND_response_visuals/ind_aoi_map.png"))

ind_response_map
```


```{r}
tmap_mode('view')

bgd_response_map <- bgd_aoi %>% 
  dplyr::select(-q_url) %>% 
  tm_shape() +
  tm_basemap(leaflet::providers$Esri.WorldImagery) +
  tm_bubbles(alpha = 0.2,
             fill = 'ip_address',
             col = 'skyblue',) +
  tm_scalebar(position = c('left', 'bottom')) +
  tm_title("Adaptation Observatory Responses, Bangladesh (2024-4-11)")


tmap_save(bgd_response_map,
        filename = here("response_analysis/response_visuals/BGD_response_visuals/bgd_aoi_map.png"))

bgd_response_map
```

### What's the most number of surveys a single ip address has submitted?
```{r}
# let's check our new column
max(bgd_demos$number_of_surverys_submitted)

max(ind_demos$number_of_surverys_submitted)
```


